### 2010-12-17 Text/paper.tex
Added a few simulations picture. Need to resolve the interface

\section{Non-axisymmetric case}
That could be fucking difficult. For example according to \cite{heil-threedim} for the capillary
number $Ca=0.01$, the radiuses converge as $r_h=0.99$ and $r_d=1.1$. Therefore one needs to resolve
as the $0.5\%$ of whole channel width to see the difference. That certainly implies so large grid
that can kill the simulation at least $200x200x3000$. However, we can refer to artificially made
interface as $1-2$ lattice Boltzmann units but keeping the capillary number as it is required. In
this case we can refer like we can't resolve the interface but we can certainly to attribute it to
the wall gradient as extreme case. The dimnesionalization case is therefore as follows:
\begin{equation}
Ca=\frac{\mu_{liq} U_{bubble}}{\gamma},
\end{equation}
therefore let us pick up the same parameters as for the previous case. To perform simulations we
started with the following parameters as
$k=0.04$,$A=0.04$,$\Gamma=1.0$,$N_x\mathrm{x}N_y\mathrm{x}N_z=52\mathrm{x}52\mathrm{x}750$.The
initialized density was chosen as $w=2.5$ lattice Boltzmann units. For underresolved schemes, the
pressure gradient doesn't work in the way we expect. Therefore, we take pressure gradient in the
following way and later on establish the associated capillary number. In this case we can check the
extreme values for the pressure gradients and the continuous interface methods:
\begin{equation}
\frac{\mathrm{d}P}{\mathrm{d}x}=
\begin{cases}
1\dots10\mathrm{x}10^{-6}\\
10,15\dots 100 \mathrm{x}10^{-6}
\end{cases}
\end{equation}

>>>>

\section{Non-axisymmetric case}
For example according to \cite{heil-threedim} for the capillary
number $Ca=0.01$, the radiuses converge as $r_h=0.99$ and $r_d=1.1$. Therefore one needs to resolve
as the $0.5\%$ of whole channel width to see the difference. That certainly implies so large grid
that can kill the simulation at least $200x200x3000$. However, we can refer to artificially made
interface as $1-2$ lattice Boltzmann units but keeping the capillary number as it is required. In
this case we can refer like we can't resolve the interface. However, one can check whether
completely underresolved interfaces can give something good with the continuous interface methods.
The dimensionalization case is therefore as follows. Instead of starting with the capillary number
simulations we initialize the initial thickness with $2.5$ lattice boltzmann units, change the
pressure gradients through the following numbers:
\begin{equation}
\frac{\mathrm{d}P}{\mathrm{d}x}=
\begin{cases}
1\dots10\mathrm{x}10^{-6}\\
10,15\dots 100 \mathrm{x}10^{-6}
\end{cases}
\end{equation}
After performing the simulations we determine the $R_{axis}$, $R_{diag}$ versus calculated
capillary number
\begin{equation}
Ca=\frac{\mu_{liq} U_{bubble}}{\gamma}.
\end{equation}
To perform simulations we
started with the following parameters as
$k=0.04$,$A=0.04$,$\Gamma=1.0$,$N_x\mathrm{x}N_y\mathrm{x}N_z=52\mathrm{x}52\mathrm{x}750$.
For underresolved schemes, the pressure gradient doesn't work in the way we expect. Therefore, we
take pressure gradient in the following way and later on establish the associated capillary number.
We want to keep track of $R_{diag}$ when the $R_{axis}$ is underresolved. The preliminary results
for the film thickness measured in the middle of the bubble are shown in Fig.
\ref{fig:underresolved:capillaries}. 
\begin{figure}
\includegraphics[width=0.97\textwidth]{Figures/underresolved_capillaries.eps}
\caption{The underresolved profiles axis and diagonal radiuses versus capillary numbers. $50$
percent resolution starts from $Ca=1.0$, which is quite high. One can see it's exactly where
radiuses converge instead of $Ca=0.04$. However, one can see from simulations Fig.
\ref{fig:wang:critical:capillary} and Fig.\ref{fig:thickness:variation:ca:ten} the thickness,
especially for Fig.\ref{fig:thickness:variation:ca:ten}, can significantly variate over a bubble
length. \label{fig:underresolved:capillaries}}
\end{figure}

One can see the variation of thickness over the bubble length for the given capillary $Ca=1.06$ in
Fig. \ref{fig:variation:bubble:ca:one}. One can see that variation over the length can be neglected
for relatively high $Ca$ numbers.
\begin{figure}
\includegraphics[width=0.97\textwidth]{Figures/bubble_length_ca_one.eps}
\caption{The bubble length variation over for given $Ca=1.06$.
One can see that there is no such high variation over the bubble
length. \label{fig:variation:bubble:ca:one}}
\end{figure}

\section{Steady-state case}
We want to perform understanding of the steady state regime. As well probably it's good idea to
change domain as well, to reduce the length but to insure enough length of the bubble. The
steady-state calculations are performed on $52\mathrm{x}52\mathrm{x}750$ with large enough the
interface.
